### 2021-02-24 manuscript/supplementary.tex
Updating MS.
Major update: larger dataset, revised and simplified code, new figures.

\Authors{Paul P. Gardner\textsuperscript{1,2}*, James Paterson\textsuperscript{1,2}, Fatemeh Ashari Ghomi\textsuperscript{1,2}, Sinan Uğur Umu\textsuperscript{1,2}, Stephanie McGimpsey\textsuperscript{1,2}} % Authors
\affiliation{\textsuperscript{1}\textit{School of Biological Sciences, University of Canterbury, Christchurch, New Zealand.}} % Author affiliation
\affiliation{\textsuperscript{2}\textit{Biomolecular Interaction Centre and the Bio-Protection Research Centre, University of Canterbury, Christchurch, New Zealand.}}
\affiliation{*\textbf{Corresponding author}: paul.gardner@canterbury.ac.nz} % Corresponding author

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.75\textwidth]{supplementary-figures-small.pdf}
\caption{The distributions for the measures we expected to be
  predictive of software quality used in this study. These
are, reading from left to right, top to bottom: Accuracy -- the mean
normalised accuracy rank for each benchmarked method; Speed -- the
mean normalised speed rank for each benchmarked method; Cites -- the number of
citations to the most cited manuscript describing a method, data from GoogleScholar;
JIF -- the Journal Impact Factor to the highest impact journal that has published
a manuscript describing a method, data from 2014 Thompson-Reuters Citation Reports;
JH5 -- the Journal H5 index to the highest impact journal that has published
a manuscript describing a method, data from GoogleScholar 2015 Metrics;
H-index -- the H-index for the highest profile corresponding author from the
manuscripts describing a method, data from GoogleScholar User Profiles;
M-index -- the M-index (H-index/(\#years since first publication)) for the
highest profile corresponding author from the manuscripts describing a method,
data from GoogleScholar User Profiles;}
\label{fig:metricDistributions}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.5\textwidth]{smoothScatter-speed-vs-accuracy.pdf}
\caption{A smoothed color density representation of a scatterplot of
  normalised speed ranks and normalised accuracy ranks. Dark red
  regions are indicative of of a high density of points, blue shades
  indicate the reverse. The expected inverse relationship between
  speed and accuracy is indicated with a dashed black line, points
  above this line could be considered comparatively fast and accurate,
  points below are the reverse. A locally weighted regression (lowess)
  curve is shown in red.}
\label{fig:smoothScatterAccSpeed}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.85\textwidth]{smoothScatters.pdf}
\caption{A smoothed color density representation of a scatterplot of
  journal impact factors (JIF) on the left and number of citations on
  the right vs normalised accuracy ranks. As above, dark red regions
  are indicative of of a high density of points, blue shades indicate
  the reverse. The JIF for journals that are major publishers of
  bioinformatic software are indicated on the left. }
\label{fig:smoothScatters}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.95\textwidth]{relAge-SpeedVsAccuracy-heatmap-edited.pdf}
\caption{{\bf A.} Violin plots for the relative age distribution for software tools in each of the 5 2x2 cells indicated in B. The five boxes correspond to the four extreme corners of the speed vs accuracy spectrum (i.e. slow and inaccurate, slow and accurate, fast and inaccurate, fast and accurate) and the central box (medium speed and medium accuracy). {\bf B.} A heatmap indicating the relative age of software in a range of relative accuracy and speed rankings. Blue colours indicate an abundance of older software tools in an accuracy and speed category, while light colours indicate younger software in an accuracy and speed category. }
\label{fig:ageplot}
\end{figure}

>>>>

%\Authors{Paul P. Gardner\textsuperscript{1,2}*, James Paterson\textsuperscript{1,2}, Fatemeh Ashari Ghomi\textsuperscript{1,2}, Sinan Uğur Umu\textsuperscript{1,2}, Stephanie McGimpsey\textsuperscript{1,2}} % Authors
%\affiliation{\textsuperscript{1}\textit{School of Biological Sciences, University of Canterbury, Christchurch, New Zealand.}} % Author affiliation
%\affiliation{\textsuperscript{2}\textit{Biomolecular Interaction Centre and the Bio-Protection Research Centre, University of Canterbury, Christchurch, New Zealand.}}
%\affiliation{*\textbf{Corresponding author}: paul.gardner@canterbury.ac.nz} % Corresponding author

\Authors{Paul P. Gardner\textsuperscript{1,2}*, James M. Paterson\textsuperscript{?}, Fatemeh Ashari-Ghomi\textsuperscript{?}, Sinan U. Umu\textsuperscript{?}, Stephanie McGimpsey\textsuperscript{3,4}, Aleksandra Pawlik\textsuperscript{5},
Alex Gavryushkin\textsuperscript{6}, Michael A Black\textsuperscript{1}
} % Authors

\affiliation{\textsuperscript{1}\textit{Department of Biochemistry, University of Otago, Dunedin, New Zealand.}} % Author affiliation
\affiliation{\textsuperscript{2}\textit{Biomolecular Interaction Centre, University of Canterbury, Christchurch, New Zealand.}}
\affiliation{\textsuperscript{3}\textit{McConomy School of Dance, Derry, Ireland.}}
\affiliation{\textsuperscript{4}\textit{Research for Good, Limavady, Ireland.}}
\affiliation{\textsuperscript{5}\textit{New Zealand eScience Infrastructure, 49 Symonds St, Auckland, New Zealand.}}
\affiliation{\textsuperscript{6}\textit{Department of Computer Science, University of Otago, Dunedin, New Zealand.}} % Author affiliation
\affiliation{*\textbf{Corresponding author}: paul.gardner@otago.ac.nz} % Corresponding author

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.95\textwidth]{supplementary-figures-small.pdf}
\caption{The distributions for the measures we expected to be
  predictive of software quality used in this study. These
are, reading from left to right, top to bottom: Accuracy -- the mean
normalised accuracy rank for each benchmarked method; Speed -- the
mean normalised speed rank for each benchmarked method;
JH5 -- the Journal H5 index to the highest impact journal that has published
a manuscript describing a method, data from GoogleScholar 2020 Metrics;
Cites -- the number of citations to the most cited manuscript describing a method, data from GoogleScholar;
H-index -- the H-index for the highest profile corresponding author from the
manuscripts describing a method, data from GoogleScholar User Profiles;
M-index -- the M-index (H-index/(\#years since first publication)) for the
highest profile corresponding author from the manuscripts describing a method,
data from GoogleScholar User Profiles;
Relative ages for different tools, for each benchmark tools were ranked based upon publication dates, these ranks were normalised to lie between 0 and 1.
}
\label{fig:metricDistributions}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=0.95\textwidth]{supplementary-figures-pairs.pdf}
\caption{}
\label{fig:metricPairs}
\end{figure}

@@

%% \begin{figure}[H]
%% \centering
%% \includegraphics[width=0.5\textwidth]{smoothScatter-speed-vs-accuracy.pdf}
%% \caption{A smoothed color density representation of a scatterplot of
%%   normalised speed ranks and normalised accuracy ranks. Dark red
%%   regions are indicative of of a high density of points, blue shades
%%   indicate the reverse. The expected inverse relationship between
%%   speed and accuracy is indicated with a dashed black line, points
%%   above this line could be considered comparatively fast and accurate,
%%   points below are the reverse. A locally weighted regression (lowess)
%%   curve is shown in red.}
%% \label{fig:smoothScatterAccSpeed}
%% \end{figure}

%% \begin{figure}[H]
%% \centering
%% \includegraphics[width=0.85\textwidth]{smoothScatters.pdf}
%% \caption{A smoothed color density representation of a scatterplot of
%%   journal impact factors (JIF) on the left and number of citations on
%%   the right vs normalised accuracy ranks. As above, dark red regions
%%   are indicative of of a high density of points, blue shades indicate
%%   the reverse. The JIF for journals that are major publishers of
%%   bioinformatic software are indicated on the left. }
%% \label{fig:smoothScatters}
%% \end{figure}

@@

\begin{figure}[H]
\centering
%\includegraphics[width=0.95\textwidth]{relAge-SpeedVsAccuracy-heatmap-edited.pdf}
\includegraphics[width=0.45\textwidth]{relAge-speedAcc.pdf}
\includegraphics[width=0.45\textwidth]{relAge-SpeedVsAccuracy-heatmap.pdf}
\caption{{\bf Left.} Violin plots for the relative age distribution
  for software tools in each of the 5 2x2 cells indicated in B. The
  five boxes correspond to the four extreme corners of the speed vs
  accuracy spectrum (i.e. slow and inaccurate, slow and accurate, fast
  and inaccurate, fast and accurate) and the central box (medium speed
  and medium accuracy). {\bf Right.} A heatmap indicating the relative age
  of software in a range of relative accuracy and speed rankings. Blue
  colours indicate an abundance of older software tools in an accuracy
  and speed category, while light colours indicate younger software in
  an accuracy and speed category. }
\label{fig:ageplot}
\end{figure}
